\bibitem{hecht_optics_2017} E. Hecht, \textit{Optics}, 5th ed. Pearson, 2017.

\bibitem{born_wolf_principles_1999} M. Born and E. Wolf, \textit{Principles of Optics}, 7th ed. Cambridge University Press, 1999.

\bibitem{wang_ssim_2004} Z. Wang, A. C. Bovik, H. R. Sheikh, and E. P. Simoncelli, ``Image quality assessment: from error visibility to structural similarity,'' \textit{IEEE Trans. Image Process.}, vol. 13, no. 4, pp. 600--612, 2004.

\bibitem{storn_differential_1997} R. Storn and K. Price, ``Differential evolution -- a simple and efficient heuristic for global optimization over continuous spaces,'' \textit{J. Global Optim.}, vol. 11, no. 4, pp. 341--359, 1997.

\bibitem{adelson_anamorphic_1990} E. H. Adelson and J. R. Bergen, ``The plenoptic function and the elements of early vision,'' in \textit{Computational Models of Visual Processing}, MIT Press, 1991, pp. 3--20.

\bibitem{glassner_principles_1995} A. S. Glassner, \textit{Principles of Digital Image Synthesis}. Morgan Kaufmann, 1995.

\bibitem{gonzalez_digital_2018} R. C. Gonzalez and R. E. Woods, \textit{Digital Image Processing}, 4th ed. Pearson, 2018.

\bibitem{hartley_multiple_2003} R. Hartley and A. Zisserman, \textit{Multiple View Geometry in Computer Vision}, 2nd ed. Cambridge University Press, 2003.

\bibitem{szeliski_computer_2022} R. Szeliski, \textit{Computer Vision: Algorithms and Applications}, 2nd ed. Springer, 2022.

\bibitem{do_carmo_differential_1976} M. P. do Carmo, \textit{Differential Geometry of Curves and Surfaces}. Prentice-Hall, 1976.

\bibitem{mallat_wavelet_2009} S. Mallat, \textit{A Wavelet Tour of Signal Processing}, 3rd ed. Academic Press, 2009.

\bibitem{canny_computational_1986} J. Canny, ``A computational approach to edge detection,'' \textit{IEEE Trans. Pattern Anal. Mach. Intell.}, vol. 8, no. 6, pp. 679--698, 1986.

\bibitem{otsu_threshold_1979} N. Otsu, ``A threshold selection method from gray-level histograms,'' \textit{IEEE Trans. Syst. Man Cybern.}, vol. 9, no. 1, pp. 62--66, 1979.

\bibitem{lowe_sift_2004} D. G. Lowe, ``Distinctive image features from scale-invariant keypoints,'' \textit{Int. J. Comput. Vis.}, vol. 60, no. 2, pp. 91--110, 2004.

\bibitem{milanfar_tour_2013} P. Milanfar, ``A tour of modern image filtering,'' \textit{IEEE Signal Process. Mag.}, vol. 30, no. 1, pp. 106--128, 2013.
